The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-11-02 paper/draft.tex
extend new angle for intro (complete sentence)

In the following, we present a model that remedies both of the adressed shortcomings by implementing genetic processes on a niche-explicit background
in an island biogeography framework.
We will adress the questions of what relative impact does (a) genetic linkage and (b) reproductive isolation have on emerging species numbers and diversity,
(c) what ...
We find that

>>>>

Besides adaptive radiations(/evolution), changes in or different measures of geographic isolation (landscape complexity) can give rise to non-adaptive radiations.

In the following, we present a model that remedies both of the adressed shortcomings by implementing genetic processes on a niche-explicit background
in an island biogeography framework.
We will adress the questions of what relative impact does (a) genetic linkage and (b) reproductive isolation have on emerging species numbers and diversity,
and how (c) landscape heterogeneity (habitat niche diverstiy) and (d) topographical complexity differently affect radiatons.
